\chapter*{Seznam publikací}
\addcontentsline{toc}{chapter}{Seznam publikací}

\begin{enumerate}
\item{
  Oldřich Krůza and Nino Peterek.
  Making Community and ASR Join Forces in Web Environment.
  In \textit{International Conference on Text, Speech and Dialogue},
  pages 415--421.
  Springer, 2012.
}
\item{
  Oldřich Krůza and Vladislav Kuboň.
  Second-Generation Web Interface to Correcting ASR Output.
  In Kohei Arai, Rahul Bhatia and Supriya Kapoor, editors,
  \textit{Proceedings of the Future Technologies Conference (FTC) 2018},
  number 1, pages 749--762, Cham, Switzerland, 2018.
  Science and Information Organization, Springer-Verlag.
}
\item{
  Oldřich Krůza.
  Phonetic Transcription by Untrained Annotators.
  In Stani\-slav Krajči, editor,
  \textit{Proceedings of the 18th conference ITAT 2018:
  Slovenskočeský NLP workshop (SloNLP 2018)},
  volume 2203 of \textit{CEUR Workshop Proceedings},
  pages 35--40,
  Košice, Slovakia, 2018.
  Šafárik University, Košice,
  CreateSpace Indepedent Publishing Platform.
}
\item{
  Jan Oldřich Krůza.
  Spoken Corpus of Karel Makoň.  
  In \textit{Book of Abstracts XI International Conference on Corpus Linguistics},
  pages 189--190.
  ADEIT - Fundación Universidad-Empresa de la Universitat de València, 2019.\\
  \url{https://adeit-estaticos.econgres.es/19\_CILC/book\_abstracts.pdf}
}
\item{
  Jan Oldřich Krůza.
  Czech parliament meeting recordings as ASR training data.
  In \textit{Proceedings of the 2020 Federated Conference on Computer Science
  and Information Systems (FedCSIS)},
  pages 185--188.
  IEEE.\\
  \url{https://annals-csis.org/Volume\_21/drp/119.html}
}
\item{
  Matyáš Kopp and Vladislav Stankov and Jan Oldřich Krůza and Pavel Straňák and Ondřej Bojar.
  ParCzech 3.0: A Large Czech Speech Corpus with Rich Metadata.
  In \textit{International Conference on Text, Speech and Dialogue},
  Springer, 2021.
}
%\item{
%    Jan Oldřich Krůza.
%    Restructuring Spoken Corpus for Streaming Emulation.
%    In \textit
%}
\end{enumerate}
